Case for Support

### 2021-11-17 application/detailsOfResource.tex

    \item[Interpretable latents for behavioral videos]\citep[Partitioned
        Subspace Variational Autoencoder, PS-VAE;][]{whitewayEtAl21} produces
        interpretable low-dimensional representations of behavioural videos by
        combining the output of pose-estimation algorithms (e.g., DeepLabCut)
        with unsupervised dimensionality reduction methods. These
        low-dimensional representations facilitate downstream behavioral and
        neural analyses. It is based on autoencoders and is implemented in
        Python\footnote{code for PS-VAE is embedded in the BehaveNet code
        https://github.com/themattinthehatt/behavenet.%
        % Please refer to class \texttt{PSVAE} in texttt{behavenet.models.vaes.py}.
        }. After training it can be used
        online to extract low-dimensional features and perform downstream
        processing.

@@

    \item[Gaussian Linear Dynamical
        System]\citep[(GLDS)][]{andersonAndMoore12}: with sufficiently large
        bin sizes, spike counts can be modelled as Gaussian random processes.
        This Gaussianity assumption greatly simplifies the estimation of
        parameters of linear dynamical system (LDS) models, as well as
        inferences about their states. After models' parameters have been
        learned, GLDS can be used online. A unique feature of GLDS is that the
        posterior distribution of states given all observation up to the
        present can be calculated efficiently. This estimate of the posterior
        distribution can be used online for experimental control, as we
        propose in Section~\ref{sec:comparisonOfMultipleMethods}. We will use an R implementation of GLDS
        which allows the use of external
        inputs\footnote{https://github.com/joacorapela/kalmanFilter}.

    \item[Poisson Linear Dynamical System]\citep[PLDS][]{mackeEtAl15}: for
        smaller bin sizes, spike counts are better modelled as Poisson random
        processes, rather than Gaussian ones. The algorithm described in
        \citet{mackeEtAl15} can estimate the parameters of a LDS, and make
        inferences about its states, from Poisson distributed observations.  We
        propose to interface Bonsai with a Matlab implementation of
        PLDS\footnote{https://bitbucket.org/mackelab/pop\_spike\_dyn/src/master/}
        that uses variational inference. PLDS does not provide online estimates
        of the states, since data from a full trial is needed for state
        inference.

>>>>

    \item[Interpretable latents for behavioral videos]\citep[Partitioned
        Subspace Variational Autoencoder, PS-VAE;][]{whitewayEtAl21} produces
        interpretable low-dimensional representations of behavioural videos by
        combining the output of pose-estimation algorithms (e.g., DeepLabCut)
        with unsupervised dimensionality reduction methods. These
        low-dimensional representations facilitate downstream behavioral and
        neural analyses. It is based on autoencoders and is implemented in
        Python\footnote{code for PS-VAE is embedded in the BehaveNet code\\ 
        https://github.com/themattinthehatt/behavenet.%
        % Please refer to class \texttt{PSVAE} in texttt{behavenet.models.vaes.py}.
        }. After training it can be used
        online to extract low-dimensional features and perform downstream
        processing.

@@

    \item[Gaussian Linear Dynamical
        System]\citep[(GLDS)][]{andersonAndMoore12}: with sufficiently large
        bin sizes, spike counts can be modelled as Gaussian random processes.
        This Gaussianity assumption greatly simplifies the estimation of
        parameters of linear dynamical system (LDS) models, as well as
        inferences about their states. After models' parameters have been
        learned, GLDS can be used online. A unique feature of GLDS is that the
        posterior distribution of states given all observation up to the
        present can be calculated efficiently. This estimate of the posterior
        distribution can be used online for experimental control, as we
        propose in Section~\ref{sec:comparisonOfMultipleMethods}. We will use an R implementation of GLDS
        which allows the use of external
        inputs\\ \footnote{https://github.com/joacorapela/kalmanFilter}.

    \item[Poisson Linear Dynamical System]\citep[PLDS][]{mackeEtAl15}: for
        smaller bin sizes, spike counts are better modelled as Poisson random
        processes, rather than Gaussian ones. The algorithm described in
        \citet{mackeEtAl15} can estimate the parameters of a LDS, and make
        inferences about its states, from Poisson distributed observations.  We
        propose to interface Bonsai with a Matlab implementation of
        PLDS\\ \footnote{https://bitbucket.org/mackelab/pop\_spike\_dyn/src/master/}
        that uses variational inference. PLDS does not provide online estimates
        of the states, since data from a full trial is needed for state
        inference.

### 2021-11-17 application/userEngagement.tex

In the past four years we have developed bonsai-rx.org as a hub for documentation and learning
resources (e.g. courses, video tutorials and examples) on how to use Bonsai. We have also engaged
with leading, relevant training efforts such as the CAJAL Neuroscience
Training Programme (Bonsai 0121) and the Transylvania Experimental Neuroscience
Summer School, to increase awareness of Bonsai and
its packages throughout the neuroscience community. Together with participation
at smaller invited venues, there has been an average of 5 courses in Bonsai
each year, with at least 20 students each; i.e.  around 100 neuroscience students annually are introduced to experimental tools directly through a
course in the Bonsai programming language.

Bonsai's 10th anniversary will take place in 2022. The proposed ML package will thus leverage planned venues, events, and infrastructure to disseminate
awareness throughout the community, including presentations at conferences,
workshops, and training sessions, as well as electronic newsletters, forums and
social media articles.

The proposed development will facilitate interfacing with other programming languages
such as Python, R, and MATLAB. This will therefore attract a whole new
community of Bonsai users with expertise in software development. To fully integrate this new community and provide them with the full power of Bonsai,
we plan to organise hackathons to accelerate integration of their existing data
analysis and ML algorithms and methods into Bonsai using the new
machine learning package.

>>>>

In the past four years we have developed bonsai-rx.org as a hub for documentation and learning
resources (e.g. courses, video tutorials and examples) on how to use Bonsai. We have also engaged
with leading, relevant training efforts such as the CAJAL Neuroscience
Training Programme (Bonsai 0121) and the Transylvania Experimental Neuroscience
Summer School, to increase awareness of Bonsai and
its packages throughout the neuroscience community. With participation
at smaller invited venues, there have been on average 5 Bonsai courses
each year, with at least 20 students each; i.e.  around 100 neuroscience students annually are introduced to experimental tools directly through a
course in the Bonsai programming language.

Bonsai's 10th anniversary will take place in 2022. The proposed ML package will leverage planned events, and infrastructure to disseminate
awareness throughout the community, including presentations at conferences,
workshops, and training sessions, as well as electronic newsletters, forums and
social media.

The proposed development will facilitate interfacing with other programming languages
such as Python, R, and MATLAB. This will attract a whole new
community of Bonsai users with expertise in software development. To provide these new users with the full power of Bonsai,
we plan to organise hackathons to accelerate integration of their existing data
analysis and ML algorithms and methods into Bonsai using the new
ML package.
